Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
Switch RQ1/RQ2, rephrased RQ2.

\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to
FWL controller synthesis obtain upon synthesising/verifying benchmarks that
compose the specified suite?

\item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible
solution in reasonable time considering robust stability of FWL digital
controllers?

@@

The median runtime for our benchmark set is $197$\,s, implying that \tool
can synthesise half of the controllers in less than $5$ minutes.  Overall,
the average synthesis time amounts to approximately $30$ minutes.  With
respect to RQ2 we consider these times short enough to be of practical use
to control engineers.  Regarding RQ1 we further conclude that the approach
using a two-stage verification engine is able to synthesise stable
controllers in $12$ out of the $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where the
inductive conjectures fail.  Both verification engines together enabled
controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
benchmark our approach failed to synthesise a stable controller in the
requested time limits.  This can be addressed by either increasing the fixed
point word widths considered or using floating point arithmetic instead. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

\item RQ1 \textbf{(performance)} does the CEGIS approach provide a feasible
solution in reasonable time considering robust stability of FWL digital
controllers?

\item RQ2 \textbf{(sanity check)} are the synthesised controllers sound
and can their stability be confirmed outside of our model?

@@

The median runtime for our benchmark set is $197$\,s, implying that \tool
can synthesise half of the controllers in less than $5$ minutes.  Overall,
the average synthesis time amounts to approximately $30$ minutes.  With
respect to RQ1 we consider these times short enough to be of practical use
to control engineers.  We further conclude that the approach
using a two-stage verification engine is able to synthesise stable
controllers in $12$ out of the $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where the
inductive conjectures fail.  Both verification engines together enabled
controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
benchmark our approach failed to synthesise a stable controller in the
requested time limits.  This can be addressed by either increasing the fixed
point word widths considered or using floating point arithmetic instead. 
The synthesised controllers were confirmed to be stable outside of our
model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
